\section{Conclusion}
\label{sec:conclusions}

This paper improves the original MG algorithm by two different ways: 
The first one is to remove some relaxation steps in a V-cycle, which leads to faster cycles although requires more of them to converge.
Overall, this solution achieves up to 30\% improvement although its performance enhancements vary a lot depending on the workload,
The second way to improve the algorithm is to adapt the precisions of the floating point depending on MG's precision requirements,
We use low precisions levels during the very first MG's cycles and we increase them as the execution progresses. 
Repeating this operation until reaching the maximum available accuracy available leads to significant speedups.
We estimate the benefits of these two approaches combined on different scenarios. 
When combining half-, single- and double-precisions, we can reduce by 16.4\% and 14.5\% the execution time using double- or single-precision, respectively, during the whole execution. 

In the future we plan to explore additional ideas to reduce the execution time even more like changing the precision used in different levels of a cycle. 
%However, we think that it is not
%   useful because (1) using a greater precision in the coarse levels than in the fine levels is useless as all the computations would eventually be truncated and (2) using a smaller
%   precision in the coarse levels than in the fine levels would not affect by much the execution time as, according to the measurements done, only the first 2 or 3 levels represent more than 95\% of the relaxation cost of a cycle.
Also, we plan to estimate the impact of our techniques on the energy consumption by obtaining some measurements on real machines.
Evaluating the energy consumption using different values of the $\alpha$ parameter is also in our immediate future plans.
