\documentclass[10pt,conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts,amsmath,amssymb,amsthm,amstext,latexsym}
\usepackage{subfig}
%\usepackage{mathdots}
\usepackage{url}
\usepackage{multirow}
\usepackage{tikz}
\usepackage[textwidth=2cm]{todonotes}
\usetikzlibrary{calc}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{patterns,decorations}
\newtheorem{theorem}{Theorem}
%opening

\newcommand\leo[1]{\textcolor{blue}{#1}}
\newcommand\ldo[1]{\todo[fancyline, size=\tiny, backgroundcolor=cyan]{#1}{}}

%\newcommand\leo[1]{\textcolor{black}{#1}}
%\newcommand\ldo[1]{\ignorespaces}



\pagestyle{plain}

\title{Approximating a Multi-Grid Solver}

\author{

    \IEEEauthorblockN{Valentin Le F\`{e}vre}
    \IEEEauthorblockA{
        %Barcelona Supercomputing Center\\i
        %Spain\\
        \'{E}cole Normale Supérieure de Lyon\\
        %France\\
        valentin.le-fevre@ens-lyon.fr}
    \and
    \IEEEauthorblockN{Leonardo Bautista-Gomez}
    \IEEEauthorblockA{
        Barcelona Supercomputing Center (BSC)\\
        %Spain\\
        leonardo.bautista@bsc.es}
    \and
    \IEEEauthorblockN{Marc Casas}
    \IEEEauthorblockA{
        Barcelona Supercomputing Center (BSC)\\
        %Spain\\
        marc.casas@bsc.es}
}

\begin{document}

\maketitle
\begin{abstract}

    \leo{Multi-grid methods are numerical algorithms used in parallel and
    distributed processing. The main idea of multi-grid solvers is to speedup
    the convergence of an iterative method by reducing the problem to a coarser
    grid a number of times. Multi-grid methods are widely exploited in many
    application domains, thus it is important to improve  their performance and
    energy efficiency. This paper aims to reach this objective based on the
    following observation: Given that the intermediary steps do not require
    full accuracy,} it is possible to save time and energy by reducing
    precision during some steps while keeping the final result within the
    targeted accuracy.

    \leo{To achieve this goal,} we first introduce a cycle shape different from
    the classic V-cycle used in multi-grid solvers.  Then, we propose to
    \leo{dynamically change the floating-point precision used during runtime}
    according to the accuracy needed for each intermediary step.  \leo{Our
    large scale evaluation with the } BoomerAMG multi-grid solver demonstrates
    that it is possible to trade temporary precision for time to completion.
    In particular, we are able to reach the same accuracy results as a
    double-precision floating-point algorithm while gaining 15\% improvement of
    the execution time on a GPU.\ldo{Did we actually execute it on a GPU or
    just as abstract in the model?}

\end{abstract}

\section{Introduction}
\label{sec:intro}

\input{intro.tex}

% \section{The multi-grid algorithm}
%
%\input{algo.tex}

\section{Investigate important steps in algorithm}
\label{sec:algo}

\input{investigate.tex}

\input{cycles.tex}

\section{Investigate Time-Accuracy trade-offs}
\label{sec:accuracy}

\input{newalgo.tex}

\input{proof.tex}

\input{eval.tex}

\section{Related Work}
\label{sec:related}

\input{relatedwork.tex}

\section{Conclusion}
\label{sec:conclusions}

\input{conclusion.tex}

\bibliography{biblio}
\bibliographystyle{plain}

\end{document}
