\documentclass[sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts,amsmath,amssymb,amsthm,amstext,latexsym}
\usepackage{subfig}
%\usepackage{mathdots}
\usepackage{url}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{tikz}
\usepackage[textwidth=2cm]{todonotes}
\usetikzlibrary{calc}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{patterns,decorations}
\newtheorem{theorem}{Theorem}
%opening

%\newcommand\leo[1]{\textcolor{blue}{#1}}
%\newcommand\ldo[1]{\todo[fancyline, size=\tiny, backgroundcolor=cyan]{#1}{}}

%\newcommand\marc[1]{\textcolor{red}{#1}}


\newcommand\leo[1]{\textcolor{black}{#1}}
\newcommand\ldo[1]{\ignorespaces}



\pagestyle{plain}

\title{Approximating a Multi-Grid Solver}

% \author{Valentin Le F\`{e}vre}
%     \affiliation{\'{E}cole Normale Supérieure de Lyon}
%      \email{valentin.le-fevre@ens-lyon.fr}
% 
% \author{Leonardo Bautista-Gomez}
%     \affiliation{Barcelona Supercomputing Center (BSC)}
%     \email{leonardo.bautista@bsc.es}
% 
% \author{Osman Unsal}
%     \affiliation{Barcelona Supercomputing Center (BSC)}
%     \email{osman.unsal@bsc.es}
% 
% \author{Marc Casas}
%     \affiliation{Barcelona Supercomputing Center (BSC)}
%     \email{marc.casas@bsc.es}

\begin{abstract}

    Multi-grid methods are numerical algorithms used in parallel and
    distributed processing. The main idea of multi-grid solvers is to speedup
    the convergence of an iterative method by reducing the problem to a coarser
    grid a number of times. Multi-grid methods are widely exploited in many
    application domains, thus it is important to improve  their performance and
    energy efficiency. This paper aims to reach this objective based on the
    following observation: Given that the intermediary steps do not require
    full accuracy, it is possible to save time and energy by reducing precision
    during some steps while keeping the final result within the targeted
    accuracy.

    To achieve this goal, we first introduce a cycle shape different from
    the classic V-cycle used in multi-grid solvers.  Then, we propose to
    dynamically change the floating-point precision used during runtime
    according to the accuracy needed for each intermediary step. Our evaluation
    considering a state-of-the-art multi-grid solver implementation demonstrates that it is possible to
    trade temporary precision for time to completion without hurting the
    quality if the final result.  In particular, we are able to reach the same
    accuracy results as with full double-precision while gaining between 15\%
    and 30\% execution time improvement.

\end{abstract}

\begin{document}

\maketitle

%% Section I
\input{intro.tex}

%% Section II
\input{algo.tex}


%% Section III
\input{investigate.tex}
\input{cycles.tex}

%% Section IV
\input{newalgo.tex}
\input{proof.tex}
\input{eval.tex}

%% Section VI
\input{relatedwork.tex}

%% Section VII
\input{conclusion.tex}

%% References
\bibliography{biblio}
\bibliographystyle{plain}

\end{document}
